\section{Systematics}
\label{sec:systematics}


  Apart from the uncertainties on backgrounds yields estimated from data various other sources of systematic uncertainties are considered for simulated background and signal. These uncertainties are evaluated for mode specific selection and as well as for a generalized signal selection with $\gamma+\met$ final state.

  An uncertainty of $1\%$ is considered for photon energy scale and its effects is estimated on the $A x \epsilon$.  We further estimated systematic on the \met which could be due to the variations of jet energy scale, unclustered energy scale and photon energy scale using the JetMET POG prescription as describe in ~\cite{met}. We estimated the systematic uncertainty due the jet energy scale by shifting the jet energies up and down by the recommended amounts. We have also considered  the systematic uncertainty arising from the variation in the number of interactions (pileup) in the event. Nominally, we have used the central value for the total inelastic cross section of 69.4 mb. To account for the systematic, we have shifted that value to 73.5 mb and this resulted in 1$\%$ difference in our final yields. Lastly, we apply the standard uncertainty on the integrated luminosity~\cite{LUM-13-001} of 2.6$\%$. The PDFs uncertainty on signal model is estimated 10$\%$ based on PDF4PLHC recommendations while about $3\%$ on $Z/W+\gamma$ as described in earlier section.

  It was realized that at different selection levels i.e., model-dependent and model-independent, these variation in different energy scales have different effects. We believe this is due to the window selection in photon pt in the model dependent results as discussed in following section. Therefore, we  apply different systematic uncertainty depending on the selection level.

A summary of the systematic uncertainties on $A\times \epsilon_{MC}$ of signal samples is summarized in Table:~\ref{tab:sys}

\begin{table}[htbp]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Source   & Signal & Jet Fake & Electron Fake & $\gamma$ + jet & Z$\nu\nu\gamma$ & W$\gamma$ \\
\hline
PDF & 10(0) & - & - & - & 4(4) & 4(4) \\
\hline
Luminosity & 2.6(2.6) & - & - & 2.6(2.6) & 2.6(2.6) & 2.6(2.6) \\
\hline
Photon scale $\pm$ 1 $\%$  & 4(0.5) & - & - & 4(0.5) & 4(0.5) & 4(0.5) \\
\hline
$\met$ scale & 4(2) & - & - & 4(2) & 4(2) & 4(2) \\
\hline
Jet scale & 3(2) & - & - & 5(5) & 3(2) & 3(2) \\
\hline
Pileup  &  1(1) & - & - & 1(1) & 1(1) & 1(1) \\
\hline
$Z\nu\nu\gamma$ MCFM NLO Calcution & - & - & - & - & 3(3) & - \\
\hline
$\gamma +$ jet normalization  & - & - & - & 16(16) & - & - \\
\hline
$W\gamma$ MCFM NLO Calculation & - & - & - & - & - & 3(3) \\
\hline
Jet Fake Sys   & - & 35(35) & - & - & - & - \\
\hline
Electron Fake Sys   & - & - & 6(6) & - & - & - \\
\hline
\end{tabular}
\caption{Summary of all systematic relative uncertainties in percent on $A\times \epsilon_{MC}$ calculation for Susy Higgs model (Model Independent) selection. }
\label{tab:sys}
\end{table}
